---
title: "Data management for Appsilon Ships"
author: "Marie Vaugoyeau"
date: "08/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Aim  
  
Create a shiny app with the Marine data to follow the longest trip of one selected ship with `shiny.semantic`.  
  
# Packages used  
  
```{r packages_used}
  
library(dplyr)
library(magrittr)
library(ggplot2)
library(lubridate)
library(geosphere)

```
  
  
# Import data  
  
```{r import_data}
  
ships <- readr::read_csv("raw_data/ships.csv")

ships %>% 
  glimpse()

```
  
# Check data  
  
```{r check_data}

ships %>% 
  nrow()

ships %>% 
  distinct() %>% 
  nrow()

# need to delete duplicate data
ship <- ships %>% 
  distinct()

ship %>% 
  count(SHIPNAME, SHIP_ID) %>% 
  select(SHIPNAME) %>% 
  count(SHIPNAME) %>% 
  arrange(desc(n))

```
  
Name of ships has not an unique ID... So it is impossible to use Ship Name to identify an unique ship, so user will be used ship id to find the good boat in the app.  
  
  
# Keep only true movement  
  
When ships are parked, movement is uninteresting
  
```{r need_to_select_only_true_movement}

ship %>% 
  count(is_parked)

ship %>% 
  filter(is_parked == 1) %>% 
  count(SPEED)

ship %>% 
  filter(is_parked == 0) %>% 
  ggplot() +
  aes(x = SPEED) +
  geom_histogram()

ships_in_movement <- ship %>% 
  filter(is_parked == 0) %>% 
  arrange(
    SHIP_ID,
    DATETIME
  )

```
  
# Prepare distance calculation  
  
New table with arrival and departure point.  
Distance calculation will only calculated when ship was selected.  
  
```{r table_used_in_app}

movement <- bind_cols(
  ships_in_movement %>% 
    rename(
      "latitude_departure" = "LAT",
      "longitude_departure" = "LON"
    ),
  bind_rows(
    ships_in_movement %>% 
      slice(-1) %>% 
      select(
        "latitude_end" = "LAT",
        "longitude_end" = "LON",
        "ship_id_end" = "SHIP_ID"
    ),
    tibble(
      "latitude_end" = 0,
        "longitude_end" = 0,
        "ship_id_end" = 0
    )
  )
) %>% 
  slice(-n()) %>% 
  mutate(
    good_ship = 
      case_when(
        SHIP_ID == ship_id_end ~ "yes",
        TRUE ~ "no"
      )
  ) %>% 
  filter(
    good_ship == "yes"
  ) %>% 
  select(
    - is_parked,
    - ship_id_end,
    - good_ship
  )

## To do in app
distance <-
  purrr::map(
    .x = 1:nrow(movement),
    .f = ~ distGeo(
      movement %>% select(longitude_departure, latitude_departure) %>% slice(.x),
      movement %>% select(longitude_end, latitude_end) %>% slice(.x)
    ) %>%
      as_tibble()
  ) %>%
  bind_rows() %>%
  rename(
    "distance" = "value"
  )

ship_movement <- 
  bind_cols(
    movement,
    distance
  )

save(
  ship_movement,
  file = "ship_movement.RData"
)

```

  
# Traduction from .Rmd to .R  
  
```{r traduction_in_r}

# knitr::purl("DataManagement.Rmd", documentation = 2)

```
  
